Parsing Postfix Log Files

### 2009-08-26 doc/logparser-acronyms.tex
Changes made after final checks.
Added a brief explanation of regex after its first occurrence, and added it to the glossary, as required by Howard Hamilton.

@@

\newglossaryentry{RFC}{
    type=\acronymtype,
    name={RFC},
    description={Request For Comments},
    first={Request For Comments (RFC)}
}
\newglossaryentry{RFC glossary}{
    name={Request For Comments},
    description={
        \glsreset{RFC}The \acronym{RFC} series is a series of proposals
        defining various protocols and file formats, e.g.\
        \acronym{SMTP}\@.  The name is somewhat misleading nowadays:
        initially the authors were asking for peer review, but these
        documents are now the de facto standards the Internet runs on.
    }
}

>>>>

\newglossaryentry{regex}{
    type=\acronymtype,
    name={regex},
    description={Regular Expression},
    first={Regular Expression (regex)}
}
\newcommand{\regexglossarydescription}[0]{
    Regular Expressions are a compact, powerful method of specifying
    patterns that describe a set of strings.  The regex \texttt{aa*b*b}
    describes a set of strings, all of which start with \texttt{a},
    followed by any number of \texttt{a}, then any number of \texttt{b},
    and finish with \texttt{b}; the strings \texttt{ab},
    \texttt{aaaaaaaab}, and \texttt{aaabbbbb} are members of that set,
    whereas the strings \texttt{abba}, \texttt{abcd}, and \texttt{qwerty}
    are not.  A string can be checked against a regex to determine if the
    string is a member of the set of strings described by that regex.
}
\newglossaryentry{regex glossary}{
    name={Regular Expression},
    description={
        \regexglossarydescription{}%
    }
}

@@

\newglossaryentry{RFC}{
    type=\acronymtype,
    name={RFC},
    description={Request For Comments},
    first={Request For Comments (RFC)}
}
\newglossaryentry{RFC glossary}{
    name={Request For Comments},
    description={
        \glsreset{RFC}The \acronym{RFC} series is a series of proposals
        defining various protocols and formats, e.g.\ \acronym{SMTP}\@.
        The name is somewhat misleading nowadays: initially the authors
        were asking for peer review, but these documents are now the de
        facto standards the Internet runs on.
    }
}

### 2009-08-26 doc/logparser-other-parsers-review.tex
Added a brief explanation of regex after its first occurrence, and added it to the glossary, as required by Howard Hamilton.

\acronym{LMA} requires major changes to the parser code to parse new log lines
or to extract additional data.  The code is structured as a long series of
blocks that each handle all log lines matching a single regex, so parsing
new log lines requires modifying an existing regex or carefully inserting a
new block in the correct place; extracting extra data would require
modifying multiple blocks, regexes, or both.

>>>>

\acronym{LMA} requires major changes to the parser code to parse new log
lines or to extract additional data.  The code is structured as a long
series of blocks that each handle all log lines matching a single
\acronym{regex}, so parsing new log lines requires modifying an existing
regex or carefully inserting a new block in the correct place; extracting
extra data would require modifying multiple blocks, regexes, or both.
\regexglossarydescription{}
